---
title: "Exploring Black Friday Sales Data"
author: "Muhsina Elampilakkattil"
date: "7 December 2018"
output: 
  html_document:
    toc: true
    fig_height: 4
    fig_width: 6
    code_folding: hide
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Introduction

##About the Dataset

The dataset here is a sample of the transactions made in a retail store. The store wants to know the better customer purchase behaviour against different products. Specifically, here the problem is a regression problem where we are trying to predict the dependent variable (the amount of purchase) with the help of the information contained in the other variables.

Classification problem can also be settled in this dataset since several variables are categorical, and some other approaches could be "Predicting the age of the consumer" or even "Predict the category of goods bought". This dataset is also particularly convenient for clustering and maybe find different clusters of consumers within it.

537577 obs. of  12 variables

We have to load some libraries and datasets.

```{r, message=FALSE}
#Load libraries
library(tidyverse)
library(cowplot)

#Load Black friday sales data
data<- read_csv("datasets/BlackFriday.csv")

```